Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-07-10 main.tex
Final version

\begin{abstract}

    Robots for education are not limited to support ICT teaching, and they are
    indeed finding new roles in the classroom. This article reports on such a
    new paradigm for educative robots, that involves \emph{learning by teaching}
    and strong \emph{social engagement} to help children struggling with
    handwriting. Our system relies on machine-learning and child-robot
    interaction with a small humanoid robot, and we present several real-world
    studies in schools and with occupational therapists that led us to promising
    initial results.

\end{abstract}

>>>>

%\begin{abstract}
%
%    Robots for education are not limited to support ICT teaching, and they are
%    indeed finding new roles in the classroom. This article reports on such a
%    new paradigm for educative robots, that involves \emph{learning by teaching}
%    and strong \emph{social engagement} to help children struggling with
%    handwriting. Our system relies on machine-learning and child-robot
%    interaction with a small humanoid robot, and we present several real-world
%    studies in schools and with occupational therapists that led us to promising
%    initial results.
%
%\end{abstract}
